Higher order unification for free!

### 2024-04-05 paper/main.tex
sketch conclusion

\section{Problem statement} %%%%%%%%%%%%%%%%%%%%%%
\label{sec:problem-statement}

@@

\noindent
This choice would underuse the logic programming engine provided by
the metalanguage since by removing any datum from the head of rules
indexing degenerates. Moreover the unification procedure built in the
meta language is likely to be faster than one implemented in it,
especially if the meta language is interpreted as Elpi is.

@@

\section{Alternative encodings and related work}\label{sec:encodings}

@@

\section{Practical example}

@@

>>>>

\section{Problem statement and solution} %%%%%%%%%%%%%%%%%%%%%%
\label{sec:problem-statement}

@@

\noindent
This choice would underuse the logic programming engine provided by
the meta-language since, by removing any datum from the head of rules,
indexing degenerates. Moreover the unification procedure \elpiIn{unif}
programmed in the meta-language is likely to be n order of magnitude
slower than one that is built-in.

@@

\section{Other encodings and related work}\label{sec:encodings}

@@

\section{Actual implementation}

In this paper we show a minimized example. The full code is there.
But we also have to code things in Coq.
In Elpi we don't have a main loop, we rely on the interpreter one.
So links are constraints and progress are CHR rules.

\begin{elpicode}
link-eta bla :- suspend-condition, !, declare_constraint (link-eta bla) Vars.
link-eta bla :- progress. % solves the goal, hence the constraint is not more in L.
constraints link-beta {
  % undup
  rule (G1 ?- link-eta (uvar X LX1) T1) /
       (G2 ?- link-eta (uvar X LX2) T2) |
       relocate LX1 LX2 T2 T2' <=>
       (G1 ?- T1 = T2').
}
\end{elpicode}

@@

Benefits: less work, reuse efficient ho unif (3x faster), indexing,

Future: tabling and static analysis (reuse for ML again).

Very little is Coq specific. Applies to all OL that are not a subsystem of 
HOL, or for ML that are used for meta programming.
